Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
Consistency

\begin{table*}[h]
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.25cm}|>{\centering\arraybackslash}p{4.25cm}>{\centering\arraybackslash}p{4.25cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.1cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and our contributions. The first three rows summarizes the results for the general partitioning model, except for the last row that summarizes the results for the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

>>>>

\begin{table*}[h]
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.25cm}|>{\centering\arraybackslash}p{4.25cm}>{\centering\arraybackslash}p{4.25cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.1cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and our contributions. The table summarizes the results for the general partitioning model, except for the last row that summarizes the results for the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}
